%%%%%%%%%%%%%%%英文摘要%%%%%%%%%%%%
\enabstract

With the continuous advancement of digital transformation in manufacturing enterprises, the interactions among order processing, warehouse management, production execution, procurement collaboration and quality traceability have become increasingly close. Traditional management approaches supported by manual communication and isolated information systems often suffer from delayed information transmission, insufficient inventory visibility, low cross-department collaboration efficiency and incomplete quality tracking chains. To improve collaborative management capability in enterprise supply chains, this thesis designs and implements an enterprise supply chain collaborative management system based on Spring Boot and Vue 3. The system adopts a front-end and back-end separated architecture. Spring Security and JWT are used to implement identity authentication and role-based access control, MySQL and JPA are employed for business data persistence, and WebSocket/STOMP is introduced to support real-time message notification. In this way, multiple roles, including customers, sales administrators, warehouse administrators, production administrators, procurement administrators, suppliers, quality inspectors and system administrators, can collaborate on a unified platform.

This thesis discusses the system from the perspectives of requirement analysis, overall architecture design, business process design, database design and key function implementation. Centered on order-driven business coordination, the system establishes a closed-loop process covering sales review, warehouse delivery, production execution, procurement collaboration, quality inspection recording and quality traceability. On this basis, inventory warning and weekly plan generation mechanisms are implemented to enhance the enterprise's responsiveness to inventory risks and planning coordination problems. The thesis further analyzes representative implementation mechanisms, including role-based authorization, order-warehouse-production-quality coordination, procurement-supplier-warehouse collaboration, real-time message push, quality traceability and weekly planning. Test results indicate that the system can effectively satisfy the basic requirements of enterprise supply chain collaboration and demonstrates practical engineering value in process continuity, data consistency and business traceability.

\enkeyword{Supply Chain Collaboration; Spring Boot; Vue 3; Inventory Warning; Quality Traceability}